User-level Grid Monitoring with Inca 2

### 2007-02-23 papers/hpdc-gmw-2007/paper.tex
new reporter repositories section and some features sections
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6549 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

@@

@@

\noindent In our experience, writing and maintaining user-level tests and
performance measurements is an iterative refinement process since Grids are
dynamic and the software environment changes over time as packages are
upgraded.  It is also difficult to write and deploy a test perfectly the first
time because of portability issues and sometimes incomplete user
documentation.  For example, it may take a few iterations to determine whether
detected failures are the result of a faulty test, fault user documentation,
or a faulty system.  Realistically, this is a labor-intensive activity and
thus the amount of user-level Grid monitoring is often limited by the amount
of people resources that can be assigned to it.  However, A good goal is to
test all the commands that exist in the user documentation and/or have at
least one basic test for each software component of the Grid infrastructure.

@@

% Philosophy of user-level testing
% Practical byproducts
The goal of the Inca 2 design was to

\begin{enumerate}
\item A reporter 
\item logging in reporters
\item Given the challenges of writing portable tests and benchmarks, Inca 2 
includes a set of Perl APIs that provide convenience functions to simplify
this process.

\item Periodic tests executed by the monitoring system should be automated and
run from a standard user account.  A user GSI credential should be issued and
used by the monitoring system to test services that require authentication.  
%myproxy stuff
\item Tests should be executed locally on all Grid resources when appropriate so
that all Grid access points available to users are tested.  
\item The configuration of tests should be managed centrally in order to ensure
consistent testing of the resources, rather than by system administrators who
may not use the same information that is available to users.
\item The testing system should easily adapt to new resources and testing
requirements.  In our experience, testing has an iterative refinement process
because Grids are dynamic and the software environment changes over time as
packages are upgraded.  Furthermore, it is often difficult to write and deploy
a test perfectly the first time because of portability issues and incomplete
user documentation.   
\item System administrators should not need to know the details of the
monitoring system in order to troubleshoot problems.  When a problem is
detected the monitoring system should provide system administrators with
sufficient information to locate the problem easily and test repairs.
\item A history of test results (especially any error messages) should be
retained in order to understand the behavior of their Grid over time. This
history should be available through a flexible querying interface.
\item A running monitoring system should have a limited impact on the resources
it measures and should be secure.
\end{enumerate}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) its sample output.}
\end{figure}

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written following the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML report according to
the Inca reporter schema.  The goal of the reporter schema is to accommodate
multiple types of data and to capture information about the reporter
execution to diagnose any detected failures.  The reporter schema consists of
the following elements:

@@

The Inca agent retrieves reporters from collections called reporter
repositories that consist of reporters, required packages and libraries,
and a catalog file. Repository contents are accessible using a URL and can
be shared across multiple Inca deployments. The Inca team publishes a
reporter repository that contains reporters developed for TeraGrid.

>>>>

% Uncomment to check text length -- moves figures to end of paper -- no more
% than 10 % pages w/o figures
%\usepackage{endfloat}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
% takes away page numbers
\pagestyle{empty}

@@

\item The configuration of tests or performance measurements should be managed
centrally in order to ensure consistent testing of the resources, rather than
by system administrators who may not use the same information that is
available to users.

@@

\noindent In our experience, writing and maintaining user-level tests and
performance measurements is an iterative refinement process since Grids are
dynamic and the software environment changes over time as packages are
upgraded.  It is also difficult to write and deploy a test perfectly the first
time because of portability issues and sometimes incomplete user
documentation.  For example, it may take a few iterations to determine whether
detected failures are the result of a faulty test, fault user documentation,
or a faulty system.  Realistically, this is a labor-intensive activity and
thus the amount of user-level Grid monitoring is often limited by the amount
of people resources that can be assigned to it.  However, a good goal is to
test all the commands that exist in the user documentation and/or have at
least one basic test for each software component of the Grid infrastructure.

@@

% Philosophy of user-level testing
% Practical byproducts
The main goal of the Inca 2 design was to XXX (general, flexible, easy to
install, deploy, and
maintain, scalable, secure).
The following lists the key features of Inca 2 noting which are new features
to Inca 1 versus improved.

\item Collects a wide variety of user-level monitoring results (e.g., simple
test data to more complex performance benchmark output).  (improved)

\item Captures the context of a test or benchmark as it executes (e.g.,
executable name, inputs, source host, etc.) so that system administrators have
enough information to understand the result and can troubleshoot system
problems without having to know the internals of Inca 2. (improved)

\item Provides facilities to ease the process of writing tests or benchmarks
and deploying them into Inca 2 installations. (improved)

\item Provides facilities for sharing tests or benchmarks with other Inca 2
users in order to promote sharing of each other's expertise (new)

\item Easily adapts to new resources and monitoring requirements in order to
facilitate maintenance of a running Inca 2 deployment. (improved)

\item Stores and archives monitoring results (especially any error messages) 
in order to understand the behavior of a Grid over time. The results
are available through a flexible querying interface. (improved)

%myproxy stuff
\item A running monitoring system should have a limited impact on the resources
it measures and should be secure.
\end{enumerate}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) an output sample.}
\end{figure}

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written following the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML document or report
according to the Inca reporter schema.  The goal of the reporter schema is to
accommodate multiple types of data and to capture information about the
reporter execution to diagnose any detected failures.  The reporter schema
consists of the following elements:

@@

% What are repositories and their key features
Reporter repositories are collections that consist of reporters, required
packages and libraries (including the Perl APIs described in the previous
section), and a catalog file.  Repository contents are accessible using a URL
and designed to be shared across multiple Inca deployments.  The catalog file
follows APT's Packages.gz~\cite{apt} format and thus tar.gz dependencies such
as non-standard Perl APIs or source code can be added to reporter catalog
entries.  Inca will then automatically deploy tar.gz dependencies into a
subdirectory of its installation (more in Section~\ref{agent}).  This enables
reporters to be deployed to resources with a miniumum of effort.  Furthermore,
each package specified in the catalog is versioned.  This allows Inca to
automatically distribute reporter code updates such as bug fixes.  As such,
Inca administrators maintaining repositories need to be careful to ensure
their updates are tested and work.
% XXX Check with Jim on that

% We have a lot of reporters ready to be picked 
The Inca team publishes a reporter repository that contains 143 reporters
developed and tested for TeraGrid.  Most reporters are either version
reporters that collect version information from a softare package and
serve as a most basic unit test, unit test reporters that run a more involved
unit test, or performance benchmark reporters.  The unit and version
reporters cover software such as Grid middleware, compilers, math libraries,
data tools, and visualization tools.  The performance reporters available
currently measure data transfer and execute Grid benchmarks as described in
Section~\ref{grasp}.
